---
title: "pib - further examples"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{pib - further examples}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

This document shows further examples for the sensitivity analysis based on replication data from

Carnegie, Allison and Nikolay Marinov. 2017. “Foreign Aid, Human Rights, and Democracy
Promotion: Evidence from a Natural Experiment.” American Journal of Political Science
61(3):671–683.

and

Spenkuch, J¨org L and Philipp Tillmann. 2018. “Elite influence? Religion and the electoral
success of the Nazis.” American Journal of Political Science 62(1):19–36.



```{r setup, eval=FALSE}
library(pib)
library(estimatr)
```

### Carnegie/Marinov 2017

```{r, eval=FALSE}
data("carnegie_marinov")
y <- "new_empinxavg" 
m <- "pwt_openk" 
d <- "EV" 
z <- "l2CPcol2" 
fe <- c("ccode", "year")
```

##### Diagnostic test

```{r, eval=FALSE}
confint(lm_robust(EV ~ pwt_openk + l2CPcol2, 
                  fixed_effects = ~ ccode + year, 
                  clusters = ccode, data = carnegie_marinov), 
        level = 0.9)["pwt_openk",]
```

##### Sensitivity analysis

```{r, eval=FALSE}
out <- estimate_sensitivity(carnegie_marinov, R = 1501, outcome = y,
treat = d, inst = z, post.inst = m, fe = fe, seed = 823, parallel =
"snow", ncpus = 4)

gamma <- c(-0.02, 0.02) 
sigma <- c(0, 0.002)

bounds <- post_instrument_bounds(gamma = gamma, sigma = sigma, n.sigma
= 2, estimates = out)

plot_pib_bounds(bounds, digits = 3)
```

### Spenkuch/Tillmann 2017

```{r, eval=FALSE}
data("spenkuch_tillmann")

y <- "r_NSDAP_NOV1932_p"
d <- "r_1925C_kath"
z <- "r_kath1624"
m <- "r_1933C_arb_arbeitslos"
x <- c("r_1925C_juden", "r_1925C_others", "r_1933C_frauen", "r_M1933C_frauen",
       "r_stadtkreis", "r_1925C_logtotpop", "r_M1925C_logtotpop", "r_1933C_arbfrau",
       "r_1933C_ang_arbeitslos", "r_M1933C_ang_arbeitslos", "r_1933C_hausang_arbeitslos",
       "r_1933C_ind", "r_1933C_hand", "r_1933C_oeffprivd", "r_1933C_haus", "r_1933C_angest",
       "r_1933C_beamt", "r_1933C_arb", "r_1933C_hausang", "r_1933C_selbst",
       "r_latitude", "r_longitude", "r_distance_berlin", "r_distance_nearestcity", "r_distance_border",
       "r_distance_seaport", "r_distance_river", "r_distance_resources",
       "r_reichsmatrikel", "r_Mreichsmatrikel", "r_ecclesiastical", "r_Mecclesiastical",
       "r_distance_wittenberg",
       "r_press")
fe <- "WKNR"
```

##### Diagnostic test

```{r, eval=FALSE}
diagnostic <- lm(r_1925C_kath ~ r_kath1624 + r_gem1624 +
                   r_1925C_juden + r_M1925C_juden + r_1925C_others + r_M1925C_others +
                   r_1933C_frauen + r_M1933C_frauen + r_stadtkreis +
                   r_1925C_logtotpop + r_M1925C_logtotpop +
                   r_1933C_arbfrau + r_M1933C_arbfrau +
                   r_1933C_ang_arbeitslos + r_M1933C_ang_arbeitslos +
                   r_1933C_arb_arbeitslos + r_M1933C_arb_arbeitslos +
                   r_1933C_hausang_arbeitslos + r_M1933C_hausang_arbeitslos +
                   r_1933C_ind + r_1933C_hand + r_M1933C_ind + r_M1933C_hand +
                   r_1933C_oeffprivd + r_M1933C_oeffprivd +
                   r_1933C_haus + r_M1933C_haus +
                   r_1933C_angest + r_1933C_beamt + r_M1933C_angest + r_M1933C_beamt +
                   r_1933C_arb + r_M1933C_arb +
                   r_1933C_hausang + r_1933C_selbst + r_M1933C_hausang + r_M1933C_selbst +
                   factor(WKNR) +
                   r_latitude+r_longitude + r_distance_berlin+
                   r_distance_nearestcity + r_distance_border+
                   r_distance_seaport + r_distance_river + r_distance_resources +
                   r_reichsmatrikel + r_Mreichsmatrikel + r_ecclesiastical + r_Mecclesiastical +
                   r_distance_wittenberg +
                   r_press,

                 weights = dfST$r_wahlberechtigte_NOV1932[
                   dfST$r_MNSDAP_NOV1932_p==0 & dfST$r_M1925C_kath==0 &
                     dfST$KREIS==1],

                 data=spenkuch_tillmann[dfST$r_MNSDAP_NOV1932_p==0 & dfST$r_M1925C_kath==0 &
                             dfST$KREIS==1,])

confint(diagnostic, level = 0.9)["r_1933C_arb_arbeitslos",]
```

##### Sensitivity analysis

```{r, eval=FALSE}
outST <- estimate_sensitivity(spenkuch_tillmann, R = 1501, outcome = y,
treat = d, inst = z, post.inst = m, x = x, fe = fe, weights =
spenkuch_tillmann$r_wahlberechtigte_NOV1932, seed = 823, parallel =
"snow", ncpus = 4)

gamma <- c(-0.5, 0.5) sigma <- c(0, 1)

boundsST <- post_instrument_bounds(gamma = gamma, sigma = sigma,
estimates = outST, n.sigma = 3)

plot_pib_bounds(boundsST, annotate.sigma = "all")
```
